---
title: "Exercises-strip"
author: "Anirudh Singh"
date: "March 24, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Air quality
```{r}
library("tidyverse")
library("graphclassmate")

```


```{r}
explore <- airquality %>% 
        glimpse()
```

#Explore: Create explore/0304-strip-plot-ozone-explore.R to examine the data. Explore the ozone readings using month as the categorical variable, identify the number, type, and levels of variables, create exploratory graphs to compare distributions.

```{r}
explore %>% 
        select(Ozone,Solar.R,Wind,Temp) %>% 
        summary()
```
#looks like all of them are ratio but only can tell with further p
```{r}
dim(explore)
```


```{r}
explore %>% count(Month)
```

```{r}
 explore %>% count(Month,Ozone)%>% 
        arrange(desc(n))
```
```{r}
#need to remove NA values

airqual <- na.omit(explore)

```

```{r}
dim(airqual)
```

```{r}
 airqual %>% count(Month,Ozone)%>% 
        arrange(desc(n))
```

```{r}
 ggplot(airqual, aes(x = Month, y = Ozone)) +
        geom_point() +
        geom_jitter(width = 0, height = 0.1)      
```

#this is as good as a box plot but it tells us the lower ozone readings are in May and June. It starts to show a greater range of Ozone when July, August and Sept roll by.

# Making month categorical.


```{r}
airqual$Month <- as.factor(airqual$Month)

```
#looking at relationships between Ozone and other readings
```{r}
 ggplot(airqual, aes(x = Solar.R, y = Ozone,color=Month)) +
        geom_point() +
        geom_jitter(width = 0, height = 0.1)  
```
# The relationship does not seem very strong. 300 radiation has similar Ozone readings as 50
```{r}
ggplot(airqual, aes(x = Wind, y = Ozone,color=Month)) +
        geom_point() +
        geom_jitter(width = 0, height = 0.1) 
```
# seems like mightier the wind lesser the Ozone
```{r}
ggplot(airqual, aes(x = Temp, y = Ozone,color=Month)) +
        geom_point() +
        geom_jitter(width = 0, height = 0.1) 
```
# seems like higher temperatures lead to higher Ozone readings
```{r}
write.csv(airqual, file="airqual_raw.csv")
```
```{r}

```
